### 2014-03-20 LaTeX/RhodiumTheory.tex
added duration vars
manuscript edits

Begin this section by showing a chart that tracks the effect of conflict duration on economic performance in the aggregate. The purpose of the chart would be to show that long running conflicts are not permanently depressing economic performance.

thesis: conflicts only significantly dampens economic performance if they are a threat to major population centers. conflicts isolated in sparsely populated territories of the country have little to no effect on the whole.

@@

	Use the case study of Mexico/India as a way to explain our hypothesis:

	Or instead of relying on just one case study maybe we can walk through the example for a number of countries.

	maps: would be cool if maybe we could show the progression of a certain conflict across time and space. according to our theory what we would expect to happen as a conflict gets farther away from population centers is for econ performnace to improve. on the other hand, a conflict that moves closer and closer to population centers should lead to declined in econ performance.

>>>>

thesis: conflicts only significantly dampens economic performance if they are a threat to major population centers. conflicts isolated in sparsely populated territories of the country have little to no effect on the whole. point to the imai & weinstein paper as an example of this.

@@

	Columbia +/- (BR), Pakistan - (SM), Philippines (BR), Israel (SM), Chad (BR), Democratic Republic of Congo (SM)
	(  + = Case where conflict was close to center and economy declined; - = Case where conflict far from center and no effect on econ )
